Gravitational field calculation in spherical coordinates using variable densities in depth

### 2018-11-28 manuscript/manuscript.tex
Fix line in determination of D and delta
Add tesseroid models table

\citet{Uieda2016} compared the numerical integration of homogeneous density tesseroids
with the analytical solution of a spherical shell \citep{Mikuska2006,Grombein2013} in
order to obtain default values for the distance-size ratio $D$.
We will follow this idea but for our needs the spherical shell must
have the same density function of radius as our tesseroid model.
\citet{Lin2018} show the analytical solution of the gravitational potential generated by
a spherical shell with linear density in the radial coordinate.
We derive an expression for such gravitational potential in case the spherical shell has
an arbitrary density function in depth (Eq. \ref{eq:shell-pot} in Appendix
\ref{sec:shell}), and obtained the expressions in case of linear and exponential
density.

@@

>>>>

\citet{Uieda2016} compared the numerical integration of homogeneous density tesseroids
with the analytical solution of a spherical shell \citep{Mikuska2006,Grombein2013} in
order to obtain default values for the distance-size ratio $D$.
We will follow this idea but for our needs the spherical shell must
have the same density function of radius as our tesseroid model.
\citet{Lin2018} show the analytical solution of the gravitational potential generated by
a spherical shell with linear density in the radial coordinate.
We derive an expression for such gravitational potential in case the spherical shell has
an arbitrary density function in depth (Eq. \ref{eq:shell-pot}), and obtained the
expressions in case of linear and exponential density (see Appendix \ref{sec:shell}).

@@

\begin{table}
\caption{
    Description of the tesseroid models used to build a spherical shell and characterize
    the accuracy of the numerical integration.
    The first three columns describe the shapes of the tesseroid models: each one
    specifies the number of tesseroids on the corresponding dimension (radial,
    latitudinal, longitudinal).
    The last two columns specify the latitudinal and longitudinal size of each
    tesseroid that compose the spherical shell model.
    For each shape, we define several spherical shell models which the following
    thicknesses: 100m, 1km, 10km, 100km and 1000km.
    While the outer radius of every shell is equal to the mean Earth radius
}
\label{tab:tess-models}
\begin{tabular}{cccccc}
    Radial & Latitudinal & Longitudinal  & Total tesseroids & $L_\phi$ & $L_\lambda$
    \\ \hline
    1 & 1  & 2  & 2   & 180$^\circ$ & 180$^\circ$ \\
    1 & 6  & 12 & 72  &  30$^\circ$ &  30$^\circ$ \\
    1 & 12 & 24 & 288 &  15$^\circ$ &  15$^\circ$ \\
    1 & 18 & 36 & 648 &  10$^\circ$ &  10$^\circ$ \\
\end{tabular}
\end{table}
